---
title: "p8105_hw6_sl5010"
author: "Fiona Li"
date: "11/30/2021"
output: github_document
---

## Problem 1

```{r}
library(tidyverse)
library(modelr)
library(mgcv)
```

```{r}
## Load and clean the data for regression analysis
birthweight = read_csv("Data/birthweight.csv") %>%
mutate(babysex = as_factor(babysex))%>%
mutate(frace = as_factor(frace))%>%
mutate(malform = as_factor(malform))%>%
mutate(mrace = as_factor(mrace))
sum(is.na(birthweight))
head(birthweight) 
```
Number of missing data is **0**.

```{r}
## Propose a regression model for birthweight.
birthweight %>% 
  lm(bwt ~ babysex+bhead+blength+delwt+fincome+frace+gaweeks+malform+menarche+mheight+momage+mrace+parity+pnumlbw+pnumsga+ppbmi+ppwt+smoken+wtgain, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

**Describe your modeling process:**at $\alpha = 0.05$, we choose the significant factors: parity, mrace, gaweeks, babysex, bhead, blength and delwt

```{r}
## get model 1
model1 = 
birthweight %>%
  lm(bwt ~ parity + mrace + gaweeks+babysex+bhead+blength+delwt, data = .)
modelr::add_residuals(birthweight, model1)
modelr::add_predictions(birthweight, model1)
birthweight %>% 
  modelr::add_residuals(model1) %>%
  modelr::add_predictions(model1) %>%
  ggplot(aes(x = pred, y = resid)) + geom_point(alpha = .3) + labs(title = "plot of model residuals against fitted values")
```

```{r}
main_effects_model = lm(bwt ~ blength +gaweeks, data = birthweight)
three_way_interaction_model=  lm(bwt ~ bhead*blength*babysex, data = birthweight)
```

```{r}
cv_df =
  crossv_mc(birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
cv_df = 
  cv_df %>% 
  mutate(
    model1  = map(train, ~lm(bwt ~ parity + mrace + gaweeks+babysex+bhead+blength+delwt, data = .x)),
    main_effects_model = map(train, ~lm(bwt ~ blength +gaweeks, data = .x)),
    three_way_interaction_model = map(train, ~gam(bwt ~ bhead*blength*babysex, data = as_tibble(.x)))) %>% 
  mutate(
    rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
    rmse_main_effects_model = map2_dbl(main_effects_model, test, ~rmse(model = .x, data = .y)),
    rmse_three_way_interaction_model = map2_dbl(three_way_interaction_model, test, ~rmse(model = .x, data = .y)))
```

```{r}
## get the plot
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin() + labs(title = "comparison in terms of the cross-validated prediction error")
```

discribe: I found that my model has lowest cross-validated prediction error, which means my model 1 is the most accurate, followed by three_way_interaction_model. main_effects_model is the most inaccurate model.

## Problem 2

```{r}
## getting the data
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
 bootstrap_results = 
 weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) 

bootstrap_results %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))%>% 
  knitr::kable(digits = 3)

bootstrap_logresults = 
bootstrap_results %>%  
  select(term,.id,estimate) %>%
  pivot_wider(
    names_from = term,
    values_from = estimate) %>%
  rename(Intercept = "(Intercept)") %>%
  mutate(log_estimate = log(Intercept*tmin))

bootstrap_logresults %>% 
  summarize(
    ci_lower = quantile(log_estimate, 0.025), 
    ci_upper = quantile(log_estimate, 0.975))

bootstrap_logresults %>%
   ggplot(aes(x = log_estimate)) + geom_density()
```

**the distribution of estimates**, the $\log(\beta_0\times \beta_1)$ has the distribution that peaks at $\log(\beta_0\times \beta_1)=2.01$, where the density is 17.

```{r}
 bootstrap_results2 = 
 weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) 

bootstrap_results2 %>% 
  summarize(
    ci_lower = quantile(r.squared, 0.025), 
    ci_upper = quantile(r.squared, 0.975))

 bootstrap_results2 %>%
   ggplot(aes(x = r.squared)) + geom_density()
```

**the distribution of estimates**, the $\hat r ^2$ has the distribution that peaks at $\hat r ^2=0.91$, where the density is around 46.
